\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-17 distributed-estimation.tex
Finished writing major proofs and fixing references. Still needs a once through

Under this assumption, we have the following theorem, which provides
a local asymptotic minimax lower bound on the efficiency of
\emph{any} non-adaptive estimator.
\begin{theorem}
  \label{theorem:non-adaptive-minimax}
  Let Assumption~\ref{assumption:detection-regions} hold, and
  let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from
  observations $B_i = \indic{X_i \in A_i}$.
  Then for $Z \sim \normal(0, 1)$ and any
  symmetric and quasi-convex function $L$,
  \begin{align*}
    & \liminf_{c \to \infty} \liminf_{n \to \infty}
    \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
    \E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right] \\
    & \qquad \qquad \qquad \qquad \geq
    \E\left[ L (Z/\sqrt{\kappa(\theta)}) \right].
  \end{align*}
\end{theorem}

Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
term $\kappa(\theta)$ provides strong lower bounds on the efficiency of any
non-adaptive estimator, and moreover, that these bounds necessarily depend
on $\theta$. This suggests that attaining any type of good (uniform)
efficiency with non-adaptive estimators will be challenging.  As a
particular consequence, for the squared error $L(x) = x^2$, for any $\delta
> 0$ and $\theta$, there exists a $c < \infty$ such that $\sup_{|\tau -
  \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
  \delta)}{n \kappa(\theta)} + o(1/n)$.
We next turn to the uniformity limitations of non-adaptive strategies.

\subsection{Non-existence of a Uniformly Optimal Strategy}

We now show that under LAN models, the optimal minimal risk $1/\eta(0)$ can
only be attained at a finite number of points within $\Theta$. This fact
implies in particular that, unlike in the adaptive setting, no distributed
estimation scheme has ARE of $\eta(0)\sigma^2$ for all $\theta \in \Theta$.

\begin{thm} \label{thm:non_existence}
Under conditions (i)-(iii) in Theorem~\ref{thm:LAN1}, assume that each $A_i$ is the union of at most $K$ intervals. The number of points $\theta \in \Theta$ satisfying $\kappa(\theta) = \eta(0)$ is at most $2K$. 
\end{thm}

\begin{proof}
See Appendix~\ref{proof:thm:non_existence}.
\end{proof}

We next consider the case where each detection region is a half-open interval, i.e., the $i$th message is obtained by comparing $X_i$ against a single threshold. As we explain next, the existence of a density for the sequence of thresholds is enough to establish local asymptotic normality and leads to a closed form expression for the precision parameter and the ARE.

@@

\subsection{Threshold Detection \label{subsec:threshold}}
Assume now that each $B_i$ is of the form
\begin{equation}
\label{eq:threshold_message}
B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
-1 & X_i > t_i,
\end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and $\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
L_n(A_1,\ldots,A_n;\theta) = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
\label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold} as $n\to \infty$ is that the empirical distribution of the threshold values converges to a probability measure. Specifically, for an interval $I \subset \mathbb R$ define
\[
\lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\]
Theorem~\ref{thm:LAN1} implies:
\begin{cor} \label{cor:LAN_thresh}
Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on $\mathbb R$. Then $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a LAN family with precision parameter
\[
\kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
\]
\end{cor}
The condition that $\lambda_n$ converges to a probability measure is satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn independently from a probability distribution $\lambda(dt)$ on $\mathbb R$. \par
Due to local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by 
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that 
\[
\sqrt{n} \left( {\theta}^{ML}_n - \theta \right) \overset{d}{\longrightarrow} \mathcal{N} \left(0, 1/\kappa(\theta) \right). 
\]
It follows that when the density of the threshold values converges to a probability measure, the ARE of the ML estimator is $\kappa(\theta)\sigma^2$, and this ARE is maximal with respect to all local alternative estimators for $\theta$. We note that ${\theta}^{ML}_n$ is given by the root of 
\begin{equation}
\label{eq:ML}
\sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) },  
\end{equation}
This root is unique since the log-likelihood function is concave. Furthermore, for any $n \in \mathbb R$, we have that ${\theta}^{ML}_n  \in [t_{(1)}, t_{(n)}]$ where $t_{(i)}$ denotes the $i$th element of $\{t_1,t_2\ldots\}$. Therefore, if $\{t_1,t_2\ldots\}$ is bounded (for example $\{t_1,t_2\ldots\} \subset \Theta$), then 
\[
\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\] 
so that the ML estimator attains the local asymptotic MSE of Corollary~\ref{cor:LA_minimax}. \par
%
Since $\eta(x)$ attains its maximum at the origin, we conclude that
\[
\kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
\]
This upper bound on $\kappa(\theta)$ implies that the ARE of any distributed estimator based on a sequence of threshold detectors does not exceed $\eta(0)\sigma^2$, a fact that agrees with the lower bound under adaptive estimation derived in Theorem~\ref{thm:adpative_lower_bound}. 
%
This upper bound on $\kappa(\theta)$ is attained only when $\lambda$ is the mass distribution at $\theta$. Since $\theta$ is apriori unknown, we conclude that estimation in the distributed setting using threshold detection is strictly sub-optimal compared to the adaptive setting. In other words, the ability to choose the threshold values in an adaptive manner based on previous messages necessarily improves relative efficiency compared to a non-adaptive threshold selection.  \par

@@

%
We conclude this section by considering the density of the threshold values that maximizes the ARE $\kappa(\theta)$ under the worst choice of $\theta \in \Theta$.

\subsection{Minimax Threshold Density}
The distribution $\lambda(dt)$ that maximizes $\kappa(\theta)$, and thus minimizes $1/\kappa(\theta)$, over the worst choice of $\theta$ in $\Theta$ is given as the solution to the following optimization problem:
\begin{align}
\label{eq:var_cvx_minimax}
\begin{split}
\mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
\\ 
\mathrm{subject~to} 
\quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
\end{split}
\end{align}
The objective function in \eqref{eq:var_cvx_minimax} is concave in $\lambda(dt)$ and hence this problem can be solved using a convex program. We denote by $\kappa^\star$ the maximal value of \eqref{eq:var_cvx_minimax} and by $\lambda^\star(dt)$ the density that achieves this maximum. Theorem~\ref{thm:LAN1} and Corollary~\ref{cor:LAN_thresh} imply that for any $\theta \in \Theta$, the ARE of any local asymptotic minimax estimator (such as the ML estimator) from $\{B_i,\,i\in N\}$ of the form \eqref{eq:threshold_message} with $t_i \sim \lambda^\star$ i.i.d. is at least $\kappa^\star$.
%
%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
%\begin{align}
%\label{eq:cvx_minimax}
%\begin{split}
%\mathrm{maximize} \quad &  K \\ 
%\mathrm{subject~to} 
%\quad &  K \leq \mathbf H\lambda \\
%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
%\end{split}
%\end{align}
%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
%\begin{rem}
%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
%\end{rem} 
\par
Figure~\ref{fig:minimax_support} illustrates an approximating to $\lambda^\star(dt)$ obtained by solving a discretized version of \eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic precision parameter $\kappa^\star$ obtained this way is illustrated in Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also illustrated in these figures is $\kappa_{\unif}$ which is the precision parameter corresponding to threshold values uniformly distribution over $\Theta = [-T,T]$, namely
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}
Corollary~\ref{cor:LAN_thresh} implies that the ARE under threshold values uniformly distributed is $\kappa_\unif \sigma^2$. \par

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
%% \begin{tikzpicture}[scale = 0.55]
%% \begin{axis}[
%% width=8cm, height=6cm,
%% xmin = -0.5, xmax=0.5, 
%% restrict y to domain = 0:100,
%% ymin = 0,
%% ymax = 1,
%% samples=10, 
%% xlabel= {$dt$},
%% xtick={-0.5,0,0.5},
%% xticklabels={-$T$, 0, $T$},
%% title = {$\sigma/T = 1/2$},
%% ytick={0,0.1,1},
%% %ylabel = {$\lambda(dt)$},
%% yticklabels={0,0.1,1},
%% line width=1.0pt,
%% mark size=1.5pt,
%% ymajorgrids,
%% xmajorgrids,
%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
%% ]
%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};

%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

%% \end{axis}
%% \end{tikzpicture}
%% %
%% \begin{tikzpicture}[scale = 0.55]
%% \begin{axis}[
%% width=8cm, height=6cm,
%% xmin = -0.5, xmax=0.5, 
%% restrict y to domain = 0:100,
%% ymin = 0,
%% ymax = 0.6,
%% samples=10, 
%% xlabel= {$dt$},
%% title = {$\sigma/T = 1/5$},
%% xtick={-0.5,0,0.5},
%% xticklabels={-$T$, 0, $T$},
%% ytick={0,0.5},
%% ylabel = {$\lambda(dt)$},
%% yticklabels={0,0.5},
%% line width=1.0pt,
%% mark size=1.5pt,
%% ymajorgrids,
%% xmajorgrids,
%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
%% ]
%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};

%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

%% \end{axis}
%% \end{tikzpicture}
%% %
%% \begin{tikzpicture}[scale = 0.55]
%% \begin{axis}[
%% width=8cm, height=6cm,
%% xmin = -0.5, xmax=0.5, 
%% restrict y to domain = 0:100,
%% ymin = 0,
%% ymax = 0.3,
%% samples=10, 
%% xlabel= {$dt$},
%% xtick={-0.5,0,0.5},
%% title = {$\sigma / T = 1/10$},
%% xticklabels={-$T$, 0, $T$},
%% ytick={0,0.2},
%% %ylabel = {$\lambda(dt)$},
%% yticklabels={0,0.2},
%% line width=1.0pt,
%% mark size=1.5pt,
%% ymajorgrids,
%% xmajorgrids,
%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
%% ]
%% \addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};

%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

%% \end{axis}
%% \end{tikzpicture}
%% %
%% \begin{tikzpicture}[scale = 0.55]
%% \begin{axis}[
%% width=8cm, height=6cm,
%% xmin = -0.5, xmax=0.5, 
%% restrict y to domain = 0:100,
%% ymin = 0,
%% ymax = 0.15,
%% samples=10, 
%% xlabel= {$dt$},
%% title = {$\sigma / T = 1/20$},
%% xtick={-0.5,0,0.5},
%% xticklabels={-$T$, 0, $T$},
%% ytick={0,0.1},
%% ylabel = {$\lambda(dt)$},
%% yticklabels={0,0.1},
%% line width=1.0pt,
%% mark size=1.5pt,
%% ymajorgrids,
%% xmajorgrids,
%% legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
%% ]
%% \addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};

%% \addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

%% \addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

%% %\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
%% \end{axis}
%% \end{tikzpicture}

>>>>

Under this assumption, we have the following theorem, which provides
a local asymptotic minimax lower bound on the efficiency of
\emph{any} non-adaptive estimator.
\begin{theorem}
  \label{theorem:non-adaptive-minimax}
  Let Assumption~\ref{assumption:detection-regions} hold, and
  let ${\theta}_n$ be an estimator of $\theta \in \Theta$ from
  observations $B_i = \indic{X_i \in A_i}$.
  Then for $Z \sim \normal(0, 1)$ and any
  symmetric and quasi-convex function $L$,
  \begin{align*}
    & \liminf_{c \to \infty} \liminf_{n \to \infty}
    \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}
    \E \left[ L\left( \sqrt{n}({\theta}_{n} - \tau) \right) \right] \\
    & \qquad \qquad \qquad \qquad \geq
    \E\left[ L (Z/\sqrt{\kappa(\theta)}) \right].
  \end{align*}
\end{theorem}
\noindent
See Appendix~\ref{sec:proof-non-adaptive-minimax} for a proof.

Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
term $\kappa(\theta)$ provides strong lower bounds on the efficiency of any
non-adaptive estimator, and moreover, that these bounds necessarily depend
on $\theta$. This suggests that attaining any type of good (uniform)
efficiency with non-adaptive estimators will be challenging.  As a
particular consequence, for the squared error $L(x) = x^2$, for any $\delta
> 0$ and $\theta$, there exists a $c < \infty$ such that $\sup_{|\tau -
  \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
  \delta)}{n \kappa(\theta)} + o(1/n)$.

Yet Theorem~\ref{theorem:non-adaptive-minimax}
limits non-adaptive strategies in stronger ways.
%%
%% \subsection{Non-existence of a Uniformly Optimal Strategy}
%%
Under the density models we have considered, with the additional
Assumption~\ref{assump:failure_rate}, we can show stronger
optimality results that adaptivity is essential for achieving
optimal convergence guarantees.
Recall the transformation~\eqref{eq:eta_def} of the
hazard rate function, $\eta(x) = \frac{f^2(x)}{F(x)(1 - F(x))}$, which
has unique maximum at $x = 0$ under Assumption~\ref{assump:failure_rate}.
When each detection region $A_n$ consists of a bounded number
of intervals, the next theorem
shows that
the optimal minimal risk $1/\eta(0)$ can
only be attained at finitely many points within $\Theta$.
In particular, distinct from the adaptive setting, no distributed
estimation scheme can achieve asymptotic variance $\eta(0)$
uniformly in $\theta \in \Theta$.

\begin{thm} \label{thm:non_existence}
  Let Assumptions~\ref{assump:failure_rate}
  and~\ref{assumption:detection-regions} hold.
  Additionally, assume that $A_i$ is the union of at most $K$
  intervals. The number of points $\theta \in \Theta$ satisfying
  $\kappa(\theta) = \eta(0)$ is at most $2K$.
\end{thm}
\noindent
See Appendix~\ref{proof:thm:non_existence} for a proof.

@@

\subsection{Threshold Detection}
\label{subsec:threshold}

We now consider consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
    -1 & X_i > t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$ define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

The condition that $\lambda_n$ converges to a probability measure is
satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn
independently from a probability distribution $\lambda(dt)$ on $\mathbb
R$.

The local asymptotic normality of $\{B_n\}_{n=1}^\infty$, the maximum
likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
\begin{equation*}
  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
  \cd \normal\left(0, 1/\kappa(\theta) \right). 
\end{equation*}
It follows that when the density of the threshold values converges to a
probability measure, the ML estimator has asymptotic variance $1 /
\kappa(\theta)$, and this is minimal. We note that ${\theta}^{ML}_n$
solves
\begin{equation}
  \label{eq:ML}
  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
\end{equation}
If the collection $\{t_1,t_2\ldots\}$ is bounded
(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
\begin{equation*}
\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\end{equation*} 
so that the ML estimator attains the local asymptotic MSE of
Theorem~\ref{thm:adpative_lower_bound}.

By Assumption~\ref{assump:failure_rate},
$\eta(x)$ attains its maximum at the origin, so we conclude that
\begin{equation*}
  \kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
\end{equation*}
Moreover, this upper bound on $\kappa(\theta)$ is attained only when
$\lambda$ is the point mass at $\theta$. Since $\theta$ is \emph{a priori}
unknown, we conclude that estimation in the distributed setting using
threshold detection is strictly suboptimal compared to the adaptive
setting; the ability to choose the thresholds $t_i$
adaptively conditional on previous messages is necessary for optimal
efficiency.

@@

\subsection{Minimax Threshold Density}

We conclude this section by considering the density of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) d\lambda(t)$.
This distribution $\lambda$ solves the
optimization problem
\begin{align}
  \label{eq:var_cvx_minimax}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align}
The objective function~\eqref{eq:var_cvx_minimax} is concave in
$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
so that by discretizing, we can approximately solve this problem using
convex optimization. We let $\kappa^\star$ denote the maximal value of
problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
achieving the maximum. By drawing thresholds
$t_i \simiid \lambda^\star$,
Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
maximum likelihood estimator
using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$.
%
%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
%\begin{align}
%\label{eq:cvx_minimax}
%\begin{split}
%\mathrm{maximize} \quad &  K \\ 
%\mathrm{subject~to} 
%\quad &  K \leq \mathbf H\lambda \\
%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
%\end{split}
%\end{align}
%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
%\begin{rem}
%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
%\end{rem}

Figure~\ref{fig:minimax_support} illustrates an approximation to
$\lambda^\star(dt)$ obtained by solving a discretized version of
\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic
precision parameter $\kappa^\star$ obtained this way is illustrated in
Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also
illustrated in these figures is $\kappa_{\unif}$, the precision
parameter corresponding to threshold values uniformly distribution over
$\Theta = [-T,T]$,
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/T = 1/2$},
ytick={0,0.1,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.1,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.6,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/T = 1/5$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,0.5},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.5},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.3,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma / T = 1/10$},
xticklabels={-$T$, 0, $T$},
ytick={0,0.2},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.2},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.15,
samples=10, 
xlabel= {$dt$},
title = {$\sigma / T = 1/20$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,0.1},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
